Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-05 paperIEEE.tex
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@102 db7c848b-7755-4df2-b763-8796797afa52

We investigated the scalability of individual compounds by running the same experiment using a varying number of render nodes (2-9), as well as one dedicated application/display node. We subsequently summed up the duration of all rendered frames for each run (\fig{fCompounds}).

In the case of volume rendering we also measured the performance of compounds under heterogeneous load, which was easily achievable by varying the number of volume samples used for each fragment (1-7), while rendering. This allowed for a consistent linear scaling of rendering load, which was randomly varied (\fig{fEqualizers}) either per frame or per node. Such a linear scaling of load per node corresponds to a scaling of resources, e.g., doubling the rendering load on a specific node corresponds to halving its available rendering resources. To the system this node would then contribute the value 0.5 in terms of {\em normalized compute resources}, as illustrated by \fig{fEqualizers} (left).

This figure gives an impression of how individual compounds perform on heterogeneous systems. In this case the tree equalizer compound performs best (\fig{fEqualizers} (left)), as it allows us to a priori define how much {\em usage} it should make of individual rendering nodes, in accordance with the expected load / the available compute resources. \fig{fEqualizers} (right), on the other hand, illustrates how compounds perform on a system where compute resources fluctuate randomly every frame, as can arguably be the case for cloud-based applications. For this scenario tile equalizer seems best suited, as it performs load balancing implicitly and does not assume coherence of available resources between frames.

>>>>

We investigated the scalability of individual decomposition modes by running the same experiment using a varying number of render nodes (2-9), as well as one dedicated application/display node. We subsequently summed up the duration of all rendered frames for each run (\fig{fCompounds}).

In the case of volume rendering we also measured the performance of decomposition modes under heterogeneous load, which was easily achievable by varying the number of volume samples used for each fragment (1-7), while rendering. This allowed for a consistent linear scaling of rendering load, which was randomly varied (\fig{fEqualizers}) either per frame or per node. Such a linear scaling of load per node corresponds to a scaling of resources, e.g., doubling the rendering load on a specific node corresponds to halving its available rendering resources. To the system this node would then contribute the value 0.5 in terms of {\em normalized compute resources}, as illustrated by \fig{fEqualizers} (left).

This figure gives an impression of how individual modes perform on heterogeneous systems. In this case the tree equalizer performs best (\fig{fEqualizers} (left)), as it allows us to a priori define how much {\em usage} it should make of individual rendering nodes, in accordance with the expected load / the available compute resources. \fig{fEqualizers} (right), on the other hand, illustrates how decomposition modes perform on a system where compute resources fluctuate randomly every frame, as can arguably be the case for cloud-based applications. For this scenario tile equalizer seems best suited, as it performs load balancing implicitly and does not assume coherence of available resources between frames.
